Verifying Demonstrations

### 2018-11-22 paper/adversary-model.tex

\begin{adversaries}
\item\label{base-adversary}
  \emph{Base adversary}:
  The adversary controls \(W\) and \(S\); the adversary thus learns everything 
  that they do, but can also correlate what he learns from \(W\) and \(S\).
  \(W\) and \(S\) only learn the protocol data --- no auxiliary data.
\end{adversaries}

>>>>

\begin{adversaries}
\item\label{base-adversary}
  \emph{Base adversary}:
  The adversary controls \(W\) and \(S\); the adversary thus learns everything 
  that they do, but can also correlate what he learns from \(W\) and \(S\).
  \(W\) and \(S\) only learn the protocol data --- no auxiliary data.

\item\label{deanonymizing-witness-adversary}
  \emph{Deanonymizing-witness adversary}:
  The situation is the same as in \cref{base-adversary}, but now the witness 
  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
  (\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still does not learn \(P\)'s identity.

\item\label{deanonymizing-adversary}
  \emph{Fully deanonymizing adversary}:
  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
\end{adversaries}
